### 2017-05-31 paper.tex
abstract #61 and author summary #62

\fixme{61}{Write abstract}

@@

\fixme{62}{Write author summary}

>>>>

Technical lessons development is hindered by several core problems. 
Lessons can quickly become outdated, buggy, or fail to be updated. 
Collaborative code development offers a pathway forward, allowing us to 
create lessons which are both open and accessible, as well as 
being continually maintained, refined, and improved by a large
community of contributors. This paper provides ten simple rules that can help
others create sustainable lessons.

@@

The model of collaborative code development presents an 
alternative model to traditional scientific lesson 
development. By leveraging a community approach, educational 
resources can be more sustainable, robust, and responsive. 
These ten simple rules outline best practices for this model of 
collaborative resource development.
